Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-28 paper.tex
Fix my email

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv.tw@gmail.com, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
}

@@

\subsection{Component}
\subsubsection{IOTA}
IOTA\cite{IOTAwhitepaper} is a cryptocurrency which the ledger does not consist of transactions grouped into blocks and stored in sequential chains, but a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}. To issue a transaction in the network, one needs to perform a small amount of Proof-of-Work (PoW) that verifies two previous transactions. Since every actor in Tangle has the same role, there is no need to offer transaction fees. Therefore, it is possible to make \textbf{micropayments} which the importance will increase in the rapidly developing IoT industry, and \textbf{zero-transactions} that one could store information securely within Tangle transactions. Moreover, this structure also enables high scalability of transactions that could resolve the drawbacks of blockchain and the concern of rapid growth of IoT devices.

\subsubsection{smart contract}
Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract. The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

\subsubsection{IPFS}

\subsubsection{Masked Authenticated Messaging}
MAM\cite{MAM} is one of the best features of IOTA, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network. The consensus algorithm of IOTA ensures data integrity. These properties allow MAM to meet the requirements of both data integrity and privacy.

IOTA only allows one message per transaction and couldn't publish continuous related messages because it is easy for an attacker to issue spam transactions if the same address is used. However, MAM publishes each message to a different addresses, and each can be derived from the previous one, this mechanism protects the channel from spamming and allows us to have access to all information with channel root only. Furthermore, MAM can be used in 3 ways to control visibility and access which are public, restricted and private. In our system, restricted MAM channel is used to achieve data authoriazation between providers and consumers.

\subsubsection{TangleID}
TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint. In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs) defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system. Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication. With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.

\subsubsection{blind signature}

>>>>

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
}

@@
